R Packages to Aid in Handling Web Access Logs

### 2015-12-26 paper/paper.Rmd
update

\pkg{urltools} contains \code{url_parse} - which does the same thing as the equivalent \pkg{httr} functionality, but in a vectorised way, relying on compiled code, and producing a data.frame. Within the context of parsing and processing access logs, this is far more useful, because it works efficiently over large sets: httr's functionality, which was never designed with vectorisation in mind, does not. Indeed, benchmarking showed that \code{url\_parse} is approximately 570 times faster than httr's equivalent function:

>>>>

\pkg{urltools} contains \code{url\_parse} - which does the same thing as the equivalent \pkg{httr} functionality, but in a vectorised way, relying on compiled code, and producing a data.frame. Within the context of parsing and processing access logs, this is far more useful, because it works efficiently over large sets: httr's functionality, which was never designed with vectorisation in mind, does not. Indeed, benchmarking showed that \code{url\_parse} is approximately 570 times faster than httr's equivalent function:

### 2015-12-26 paper/paper.tex
update

A vector of URLs passed into \texttt{url\_parse} produces a data.frame,
with one column for each of the IETF-supported components, and empty
strings representing components that could not be found. Additionally,
influenced by the style of the \emph{lubridate} package
\citep{lubridate}, \texttt{urltools} contains functions to get or
\emph{set} individual components:

>>>>

A vector of URLs passed into \code{url\_parse} produces a data.frame,
with one column for each of the IETF-supported components, and empty
strings representing components that could not be found. Additionally,
influenced by the style of the \CRANpkg{lubridate} package
\citep{lubridate}, \pkg{urltools} contains functions to get or
\emph{set} individual components:
